Estimating duration in the presence of misclassification

### 2024-07-29 biology-data.tex
Rob p46 comment
Christl comment on semicolons

Of the 738 contacts enrolled, 172 (23\%) had at least one positive test.
\Textcite{hakkiOnset} analysed the 57 contacts who tested positive for SARS-CoV-2 and had the growth phase in their viral load measured.
They excluded the remaining 115 contacts with at least one positive RT-PCR test, ATACCC did not capture the phase of the infection with increasing viral load.
This exclusion was to ensure viral load trajectories are identifiable.
The 57 contacts were divided into two groups.
The first, consisting of 32 individuals, were unvaccinated and infected with a variety of varients.
The second, consisting of the remaining 25 individuals, were vaccinated and all infected with the Delta variant.
I will revisit and extend \textcite{hakkiOnset}'s analysis in \cref{E-ATACCC}, using the same 57 contacts and groups.
The first group is more relevant to the period of interest in this thesis, and I focus on this group.

@@

The beta-binomial distribution is overdispersed relative to the binomial distribution.
Overdispersion allows for household clustering and other overdispersion in the data, which is common in epidemiological data~\autocite{griffithsBBD}.
The parameterization of the beta-binomial that I use (detailed in \cref{E-distributions}) has an overdispersion parameter $\rho$, regarded as a nuisance parameter in this context.
$\rho=0$ means the beta-binomial coincides with the binomial distribution.
As $\rho \to \infty$, the distribution tends towards the uniform distribution on $[0, 1]$~\autocite{hughesUsing}.

>>>>

Of the 738 contacts enrolled, 172 (23\%) had at least one positive test.
\Textcite{hakkiOnset} analysed the 57 contacts who tested positive for SARS-CoV-2 and had the growth phase in their viral load measured.
They excluded the remaining 115 contacts with at least one positive RT-PCR test where ATACCC did not capture the phase of the infection with increasing viral load.
This exclusion was to ensure viral load trajectories are identifiable.
The 57 contacts were divided into two groups.
The first, consisting of 32 individuals, were unvaccinated and infected with a variety of varients.
The second, consisting of the remaining 25 individuals, were vaccinated and all infected with the Delta variant.
I will revisit and extend \textcite{hakkiOnset}'s analysis in \cref{E-ATACCC}, using the same 57 contacts and groups.
The first group is more relevant to the period of interest in this thesis, and I focus on this group.

@@

The beta-binomial distribution is overdispersed relative to the binomial distribution.
Overdispersion allows for household clustering and other overdispersion in the data, which is common in epidemiological data~\autocite{griffithsBBD}.
The parameterization of the beta-binomial that I use (detailed in \cref{E-distributions}) has an overdispersion parameter $\rho$, regarded as a nuisance parameter in this context.
$\rho=0$ means the beta-binomial coincides with the binomial distribution.
As $\rho \to \infty$, the beta component of the beta-binomial distribution tends towards the uniform distribution on $[0, 1]$~\autocite{hughesUsing}.

### 2024-07-29 introduction.tex
Christl comment on semicolons

All pandemics start as an \emph{outbreak}, a sudden and unexpected rise in the number of people with a disease in a local area; if this spreads over a larger geographic area (\eg a country) it becomes an \emph{epidemic}; if it spreads globally then it is a \emph{pandemic}~\autocite{grennanPandemic}.
The precise meaning of these terms varies, they are defined implicitly by their usage rather than formal definitions~\autocite{morensPandemic,doshiElusive}.
I will refer to the SARS-CoV-2 epidemic within England (or the UK), and the global impact as the pandemic.

>>>>

All pandemics start as an \emph{outbreak}, a sudden and unexpected rise in the number of people with a disease in a local area; if this spreads over a larger geographic area (\eg a country) it becomes an \emph{epidemic}; if it spreads globally then it is a \emph{pandemic}~\autocite{grennanPandemic}.
The precise meaning of these terms varies; they are defined implicitly by their usage rather than formal definitions~\autocite{morensPandemic,doshiElusive}.
I will refer to the SARS-CoV-2 epidemic within England (or the UK), and the global impact as the pandemic.
